Symbolic Weighted Language Models and\\ Quantitative Parsing over Infinite Alphabets

### 2021-07-19 main.tex
revise examples. 1 passe

\begin{example}\label{ex:nested-word}
The score representation $O$ in Example~\ref{ex:running}
is a nested-word of~$\Delta^*$.
$\Deltai$ corresponds to timed notes and continuations.
%the set of music events of the form $<\nu, \tau>$
%where $\nu$ is either a note (e.g. A4), the continuation symbol $-$, or a
%rest symbol R.
$\Deltac$ and $\Deltar$ contain respectively opening and closing parentheses.
%are used to encode the score structure:
%Let $\Deltac = \{\langle, \prec\}$ and  $\Deltar = \{\rangle, \succ\}$ where $\langle$
%(resp. $\rangle$)
%and $\prec$ (resp. $\succ$) correspond to start/end of measures, and start/end of
%tuplets. Then  \includegraphics[scale=0.20]{pictures/score5.png}
%is encoded with the nested word $\langle \prec 0, \frac{3}{4}, \frac{7}{8} \succ \rangle %\langle \prec 1, \frac{4}{3}, \frac{5}{3}  \succ \rangle$
Another example is the second candidate
\includegraphics[scale=0.35,trim=0 5mm 0 0]{pictures/ex2.pdf}
of transcription of~$I$,
linearized into
$O' =$
$\ccall{\mathsf{m}}\ts{0}$,
$\ccall{2}\ts{0}$,
$\mbox{\footnotesize A4}\ts{0}$,
$\ccall{2}\ts{\frac{1}{2}}$,
$-\ts{\frac{1}{2}}$,
$\mbox{\footnotesize B4}\ts{\frac{3}{4}}$,
$\creturn{2}\ts{1}$,
$\creturn{2}\ts{1}$,
$\ccall{\mathsf{m}}\ts{1}$,
$\ccall{3}\ts{1}$,
$\mbox{\footnotesize `C$\sharp$5`}\ts{1}$,
$\mbox{\footnotesize D5}\ts{1}$,
$\mbox{\footnotesize E5}\ts{\frac{4}{3}}$,
$\mbox{\footnotesize F5}\ts{\frac{5}{3}}$,
$\creturn{3}\ts{2}$,
$\creturn{\mathsf{m}}\ts{2}$,
$\creturn{\mathsf{m}}\ts{2}$
(see also Fig.~\ref{fig:score-tree}).
The symbol between quotes $\mbox{\footnotesize `C$\sharp$5`}$
represents an \emph{appogiatura}, %(grace-note),
i.e., an ornemental note with theoretical duration zero.
\endex
\end{example}

@@

Let us assume a third component in the symbols of $\Deltac$
\philippe{Je trouve l'exemple un peu confus. Je ne sais pas
quel est "l'associate time interval" d'un symbole. Je ne sais
pas à quoi fait référence "the following call transition". Je
n'ose pas trop toucher mais je crois qu'il faut revoir.}
which is the duration of the associated time interval.
It is used to check the timestamps in the symbols.
%
For instance, the following call transition starts in state
$q_{{i}/{c}}$, meaning that the current interval has number~$i$
amongst $c$ sub-intervals of duration~$\ell$ (as indicated by the stack top).
It reads a new time-division symbol~$\ccall{d}$.
The date for this symbol has to be the time $\tau$
for the previous time-division symbol read~$\ccall{c}$ (found on the stack)
plus the total duration of intervals read so far, $i \ell$, and
the new current interval duration is~$\frac{\ell}{d}$:
%
\(
\weic\bigl(q_{{i}/{c}},
           \ccall{c}\ts{\tau}\ts{\ell}, q,
           \ccall{d}\ts{\tau + i\ell}\ts{\frac{\ell}{d}}, q_{{i+1}/{c}},
           q_{{0}/{d}} \bigr) = \alpha_d
\).

\noindent
The weight of this transition is $\alpha_d$.
We can penalize \eg triplets compared to duplets with $\alpha_2 < \alpha_3$.
%
\noindent
Along with $\ccall{d}$,
the above transition pushes
the state $q_{{i+1}/{c}}$ on the stack,
to start the next sub-interval after reading $\creturn{d}$,
with:
\(
\weir\bigl(q_{{d}/{d}},
           \ccall{d}\ts{\tau}\ts{\ell}, q_{{i}/{c}},
           \,\creturn{d}\ts{\tau + d\ell}, q_{{i}/{c}} \bigr) = \one
\).

\noindent
Reading an event is done with:
\(
\weii\bigl(q_{{i}/{d}},
           \ccall{d}\ts{\tau}\ts{\ell}, q_{{j}/{c}},
           \mu\ts{\tau + i\ell}, q_{{i+1}/{d}} \bigr) = \alpha_\mu
\).
% cas des barres de mesure?
%For the case of a new measure symbol,
%$q_{1/1}$ is a special (initial) state.
The transition for starting to read the first measure is:
\(
\weiec\bigl(q_{1/1},
           \ccall{\mathsf{m}}\ts{0}\ts{1}, q_{1/1},
           q_{1/1} \bigr) = \one
\),
and for a new measure:
\(
\weic\bigl(q_{1/1},
           \ccall{\mathsf{m}}\ts{\tau}\ts{1}, q_{1/1},
           \ccall{\mathsf{m}}\ts{\tau + 1}\ts{1}, q_{1/1},
           q_{1/1} \bigr) = \one
\).
\endex
\end{example}

%\subsection{Properties}
\medskip\noindent
Similarly to \VPA~\cite{AlurMadhusudan09nested}
and \SVPA~\cite{dAntonyAlur14SVPDA},
the class of \SWVPA is closed under the binary operators of the underlying semiring.
%
\begin{proposition}\label{prop:SWVPA-product}
Let $A_1$ and $A_2$ be two \SWVPA
over the same $\Delta$, $\Semiring$ and $\bar\Phi$.
There exists two effectively constructible $\SWVPA$
$A_1 \oplus A_2$ and $A_1 \otimes A_2$,
such that for all $s \in \Delta^*$,
$(A_1 \oplus A_2)(s) = A_1(s) \oplus A_2(s)$ and
$(A_1 \otimes A_2)(s) = A_1(s) \otimes A_2(s)$.
\end{proposition}
%
\begin{proof}
We do a classical product construction, see Appendix~\ref{sec:product} for details.
%similar to the case of the Boolean semiring~\cite{dAntonyAlur14SVPDA}.
\end{proof}
\noindent
We now present a procedure for searching, for a~$\SWVPA$ $A$,
a word %$w \in \Delta^*$
of minimal weight for~$A$.
%as stated in the following proposition. %\wrt~$\leq_\oplus$,
%It requires the following property of label theories.
%
\begin{proposition}\label{th:best-search}
For a \SWVPA $A$
over $\Delta$,
$\Semiring$ commutative, bounded, total and complete, %semiring
and $\bar\Phi$ effective, %and $k$-convex, % label theory,
one can construct in PTIME a word $t \in \Delta^*$
such that $A(t)$ is minimal \wrt the natural ordering for $\Semiring$.
\end{proposition}
%\florent{total?}
%
Let $A = \< Q, P, \init, \bar\wei, \final >$.
%
We propose a Dijkstra algorithm computing,
for every $q, q' \in Q$,
the minimum, \wrt $\leq_\oplus$, of the function
$\beta_{q, q'} : t \mapsto \weight_A(\config{q}{\bot}, t, \config{q'}{\bot})$.
Let us denote by $b_\bot(q, q')$ this minimum.
By definition of $\leq_\oplus$, and since $\Semiring$ is total,
it holds that:
%
\begin{equation}\label{eq:bbot}
  b_\bot(q, q') = \bigoplus_{t\in \Delta^*}
  \textstyle
  \weight_A\bigl(\config{q}{\bot}, t, \config{q'}{\bot}\bigr).
\end{equation}
The infinite sum in~\eqref{eq:bbot} is well defined since $\Semiring$ is complete.
%
Following~\eqref{eq:SWVPA-value}, and the associativity and commutativity
and distributivity for~$\otimes$ and~$\oplus$, the minimum of~$A(t)$ is:
\begin{equation}\label{eq:min}
{\displaystyle\bigoplus_{t\in \Delta^*}} A(t)
=
{\displaystyle\bigoplus_{t\in \Delta^*}}
{\displaystyle\bigoplus_{q, q' \in Q}} \textstyle
\mathsf{in}(q) \mathop{\otimes}
\beta_{q, q'}(t)
\mathop{\otimes} \mathsf{out}(q')
=
{\displaystyle\bigoplus_{q, q' \in Q}} \textstyle
\mathsf{in}(q) \mathop{\otimes}
b_\bot(q, q')
\mathop{\otimes} \mathsf{out}(q')
\end{equation}

@@

Algorithm~\ref{algo:Dijkstra}
constructs iteratively two markings
$d_\bot : Q \times Q \to \Semiring$ and
$d_\top : Q \times P \times Q \to \Phic$,
%of the triplets $\<q, \sigma, q'>$
%of states of $A$ by weight values in $\Semiring$,
that converges eventually to $b_\top$ and $b_\bot$.
%It uses for that purpose a priority queue $P$ containing triplets of
%$Q \times \{ \bot, \top \} \times Q$.
\florent{explication Fig.~\ref{fig:best-update} (update) suivant cas de \eqref{eq:SWVPA-weight}?}
The infinite sums in the updates of $d$ in Algorithm~\ref{algo:Dijkstra},
Figure~\ref{fig:best-update}
are well defined
since~$\Semiring$ is complete.
%
% COMPLEXITY
%The algorithm performs $2.|Q|^2$ iterations until $P$ is empty,
%and each iteration has a time complexity $O(|Q|^2 . |P|)$.
\florent{complexity: detail with nb tr. and states?}
%That gives a time complexity $O(|Q|^4 . |P|)$.
%It can be reduced by implementing $P$ as a priority queue,
%prioritized by the value returned by $d$.
%** where  $T$ is the worst time complexity for an oracle computing the values
%of Definition~\ref{def:effective}.
%$|Q|^3.\log(|Q|^2)$
%
Algorithm~\ref{algo:Dijkstra}
terminates in PTIME and at termination, $d_\bot = b_\bot$ and $d_\top = b_\top$.
\florent{(see Appendix~\ref{sec:bestsearch}).}
With~\eqref{eq:min}, this ensures
its correctness. %of Algorithm~\ref{algo:Dijkstra}.
%
\begin{figure}[ht]
For all $q_0, q_3 \in Q$, %$p \in P$,
\[
\begin{array}{lcl}
%\multicolumn{3}{l}{\mathrm{For~all~} q_0, q_3 \in Q, p \in P,}\\
d_\top(q_1, p, q_3) & \opluseq &
  d_\top(q_1, p, q_2) \otimes
  \displaystyle\bigoplus_{\Deltai} \weii(q_2, p, q_3)\\
%\multicolumn{3}{l}{\quad
%\mathrm{where~} \weii(q_2, p, q_3)_a \in \Phic
%\mathrm{~is~the~partial~application~}
%x_c \mapsto \weii(q_2, x_c, p, a, q_3)}\\
%
d_\bot(q_1, p, q_3) & \opluseq &
  d_\bot(q_1, q_2) \otimes
  \displaystyle\bigoplus_{\Deltai} \weiei(q_2, q_3)\\
%
d_\top(q_0, p, q_3) & \opluseq &
  {\displaystyle\bigoplus_{\Deltac}}^2
  \bigl[ \bigl( \weic(q_0, p, p', q_1) \otimes_2
  d_\top(q_1, p', q_2) \bigr) \otimes_2
  {\displaystyle\bigoplus_{\Deltar}} \weir(q_2, p', q_3) \bigr]\\
%\multicolumn{3}{l}{\quad
%\mathrm{where~} \weic(q_0, p, p', q_1)_{c'} \in \Phic
%\mathrm{~is~the~partial~application~}
%x_c \mapsto \weic(q_0, p, x_c, c', p', q_1)}\\[2pt]
%
d_\bot(q_0, q_3) & \opluseq &
  {\displaystyle\bigoplus_{\Deltac}}
  \bigl(
  \weiec(q_0, p, q_1) \otimes
   d_\top(q_1, p, q_2) \otimes
  \displaystyle\bigoplus_{\Deltar} \weir(q_2, p, q_3)\bigr)\\
%
d_\bot(q_1, q_3) & \opluseq &
  d_\bot(q_1, q_2) \otimes
  \displaystyle\bigoplus_{\Deltar} \weier(q_2, q_3)\\
%
d_\top(q_1, p, q_3) & \opluseq &
  d_\top(q_1, p, q_2) \otimes d_\top(q_2, p, q_3),
  \mathrm{if~} \< q_2, \top, q_3> \notin P \\
%
d_\bot(q_1, q_3) & \opluseq &
  d_\bot(q_1, q_2) \otimes d_\bot(q_2, q_3), \mathrm{if~} \< q_2, \bot, q_3> \notin P \\
\end{array}
\]
%$\weii(q_2, p, q_3)_a \in \Phic$, for $a \in \Deltai$,
%is the partial application
%$x_c \mapsto \weii(q_2, x_c, p, a, q_3)$.
%
%$\weic(q_0, p, p', q_1)_{c'} \in \Phic$, for $c' \in \Deltac$,
%is the partial application
%$x_c \mapsto \weic(q_0, p, x_c, c', p', q_1)$.
\caption{Update $d_\bot$ with $\<q_1, q_2>$ or $d_\top$ with $\< q_1, p, q_2>$.}
\label{fig:best-update}
\end{figure}
%
%\noindent
%** effectively computable by hypothesis that the label theory is effective**
%\florent{REVOIR}
Thanks to the hypothesis of effectiveness of $\bar\Phi$, 
it is possible to construct suring the iteration a witness word
for Proposition~\ref{th:best-search}, 
\ie a word of $\Delta^*$ with a minimal weight \wrt $A$.

@@

Let us now apply the models and results of the previous sections %in order to define
to the problem of parsing over an infinite alphabet. %appropriate
%
%\subsection{Definition}
%
Let~$\Sigma$
and~$\Delta = \Deltai \uplus \Deltac \uplus \Deltar$
be countable input and output alphabets,
let $\< \Semiring, \oplus, \zero, \otimes, \one>$ be a
commutative, bounded, and complete \florent{total?} semiring
and let $\bar\Phi$ be an effective label theory over $\Semiring$,
containing $\Phi_\Sigma$, $\Phi_{\Sigma, \Deltai}$, as well as
$\Phii$, $\Phic$, $\Phir$, $\Phicr$
(following the notations of Section~\ref{sec:SWVPA-def}).
%
\noindent
We assume given the following input:
\begin{description}
\item[--] a \SWT $T$ over $\Sigma$, $\Deltai$, $\Semiring$, and $\bar\Phi$,
defining a measure %between words
$T: \Sigma^* \times \Deltai^* \to \Semiring$,

@@

This work can be extended in several directions. First, the
the best search algorithm could bbe generalized from $1$-best to $n$-best~\cite{Huang05kbest},
and to $k$-\emph{closed} semirings~\cite{Mohri02semiring}
(instead of \emph{bounded}, which corresponds to $0$-\emph{closed}). Second,
we believe that
the complexity bounds of the algorithms can be more precisely characterized.
Finally, the  best search algorithm presented here offline, whereas
an on-the-fly automata construction would allow for online parsing,
a suitable feature in the context of applications such as, e.g., automatic music transcription.

@@

\section{Correctness of the Best-Search Algorithm} \label{sec:bestsearch}
\input{app-bestsearch}

>>>>

\begin{example}\label{ex:nested-word}
The score representation $O$ in Example~\ref{ex:running}
is a nested-word of~$\Delta^*$.
$\Deltai$ corresponds to timed notes and continuations.
%the set of music events of the form $<\nu, \tau>$
%where $\nu$ is either a note (e.g. A4), the continuation symbol $-$, or a
%rest symbol R.
$\Deltac$ and $\Deltar$ contain respectively opening and closing parentheses.
%are used to encode the score structure:
%Let $\Deltac = \{\langle, \prec\}$ and  $\Deltar = \{\rangle, \succ\}$ where $\langle$
%(resp. $\rangle$)
%and $\prec$ (resp. $\succ$) correspond to start/end of measures, and start/end of
%tuplets. Then  \includegraphics[scale=0.20]{pictures/score5.png}
%is encoded with the nested word $\langle \prec 0, \frac{3}{4}, \frac{7}{8} \succ \rangle %\langle \prec 1, \frac{4}{3}, \frac{5}{3}  \succ \rangle$
Another example is the second candidate
\includegraphics[scale=0.35,trim=0 5mm 0 0]{pictures/ex2.pdf}
of transcription of~$I$,
linearized into
$O' =$
$\ccall{\mathsf{m}}\ts{[0,1]}$,
$\ccall{2}\ts{[0,1]}$,
$\mbox{\footnotesize A4}\ts{0}$,
$\ccall{2}\ts{[\frac{1}{2},1]}$,
$-\ts{\frac{1}{2}}$,
$\mbox{\footnotesize B4}\ts{\frac{3}{4}}$,
$\creturn{2}\ts{1}$,
$\creturn{2}\ts{1}$,
$\ccall{\mathsf{m}}\ts{[1,2]}$,
$\ccall{3}\ts{[1,2]}$,
$\mbox{\footnotesize `C$\sharp$5`}\ts{1}$,
$\mbox{\footnotesize D5}\ts{1}$,
$\mbox{\footnotesize E5}\ts{\frac{4}{3}}$,
$\mbox{\footnotesize F5}\ts{\frac{5}{3}}$,
$\creturn{3}\ts{2}$,
$\creturn{\mathsf{m}}\ts{2}$,
$\creturn{\mathsf{m}}\ts{2}$
(see also Fig.~\ref{fig:score-tree}).
The symbol between quotes $\mbox{\footnotesize `C$\sharp$5`}$
represents an \emph{appogiatura}, %(grace-note),
i.e., an ornemental note with theoretical duration~0.
\endex
\end{example}

@@

%Let us assume a third component in the symbols of $\Deltac$
%\philippe{Je trouve l'exemple un peu confus. Je ne sais pas
%quel est "l'associate time interval" d'un symbole. Je ne sais
%pas à quoi fait référence "the following call transition". Je
%n'ose pas trop toucher mais je crois qu'il faut revoir.}
%which is the duration of the associated time interval.
%It is used to check the timestamps in the symbols.
%
For instance, the following call transition starts in state
$q_{{i}/{c}}$, meaning that the current interval has number~$i$
amongst $c$ sub-intervals of duration~$\ell$ (as indicated by the stack top).
It reads a new time-division symbol~$\ccall{d}$:
\(
\weic\bigl(q_{{i}/{c}},
           \ccall{c}\ts{[\tau, \tau+\ell]}, q,
           \ccall{d}\ts{\iota}, q_{{i+1}/{c}},
           q_{{0}/{d}} \bigr) = \alpha_d
\).
The time interval $\iota$ attached to the~$\ccall{d}$ read 
must have a starting time $\tau + \frac{i\ell}{c}$,
where~$\tau$ and~$\ell$ are respectively
the starting time and duration of the interval attached to
the previous time-division symbol read $\ccall{c}$ (found on the stack).
%plus the total duration of intervals read so far, $i \ell$, and
%the new current interval duration is~$\frac{\ell}{d}$.
%
And it must have a duration $\frac{\ell}{d}$.

\noindent
The weight of the above transition is $\alpha_d$.
We can penalize \eg triplets compared to duplets with $\alpha_2 < \alpha_3$.
%
\noindent
Along with $\ccall{d}$,
the above transition pushes
the state $q_{{i+1}/{c}}$ on the stack,
in order to start the next sub-interval after reading $\creturn{d}$,
with the transition:
\(
\weir\bigl(q_{{d}/{d}},
           \ccall{d}\ts{[\tau, \tau+\ell]}, q_{{i+1}/{c}},
           \,\creturn{d}\ts{\tau + \ell}, q_{{i+1}/{c}} \bigr) = \one
\).

\noindent
Reading an event is done with:
\(
\weii\bigl(q_{{i}/{d}},
           \ccall{d}\ts{[\tau, \tau+\ell]}, q_{{j}/{c}},
           \mu\ts{\tau + \frac{i\ell}{d}}, q_{{i+1}/{d}} \bigr) = \alpha_\mu
\).
% cas des barres de mesure?
%For the case of a new measure symbol,
%$q_{1/1}$ is a special (initial) state.
The transition to start reading the first measure is:
\(
\weiec\bigl(q_{1/1},
           \ccall{\mathsf{m}}\ts{[0, 1]}, q_{1/1},
           q_{1/1} \bigr) = \one
\),
and for a new measure:
\(
\weic\bigl(q_{1/1},
          \ccall{\mathsf{m}}\ts{[\tau-1, \tau]}, q_{1/1},
          \ccall{\mathsf{m}}\ts{[\tau, \tau+1]}, q_{1/1},
          q_{1/1} \bigr) = \one
\).
\endex
\end{example}

%\subsection{Properties}
\medskip\noindent
Similarly to \VPA~\cite{AlurMadhusudan09nested}
and \SVPA~\cite{dAntonyAlur14SVPDA},
the class of \SWVPA is closed under the binary operators of the underlying semiring.
%
\begin{proposition}\label{prop:SWVPA-product}
Let $A_1$ and $A_2$ be two \SWVPA
over the same $\Delta$, commutative $\Semiring$ and effective $\bar\Phi$.
There exists two effectively constructible $\SWVPA$
$A_1 \oplus A_2$ and $A_1 \otimes A_2$,
such that for all $s \in \Delta^*$,
$(A_1 \oplus A_2)(s) = A_1(s) \oplus A_2(s)$ and
$(A_1 \otimes A_2)(s) = A_1(s) \otimes A_2(s)$.
\end{proposition}
%
\begin{proof}
We do a classical product construction, see Appendix~\ref{sec:product} for details.
%similar to the case of the Boolean semiring~\cite{dAntonyAlur14SVPDA}.
\end{proof}
\noindent
We now present a procedure for searching, for a~$\SWVPA$ $A$,
a word %$w \in \Delta^*$
of minimal weight for~$A$.
%as stated in the following proposition. %\wrt~$\leq_\oplus$,
%It requires the following property of label theories.
%
\begin{proposition}\label{th:best-search}
For a \SWVPA $A$
over $\Delta$,
$\Semiring$ commutative, bounded, total and complete, %semiring
and $\bar\Phi$ effective, %and $k$-convex, % label theory,
one can construct in PTIME a word $t \in \Delta^*$
such that $A(t)$ is minimal \wrt the natural ordering $\leq_\oplus$ for $\Semiring$.
\end{proposition}
%\florent{total?}
%
Let $A = \< Q, P, \init, \bar\wei, \final >$.
%
We propose a Dijkstra algorithm computing,
for every $q, q' \in Q$,
the minimum, \wrt $\leq_\oplus$, of the function
$\beta_{q, q'} : t \mapsto \weight_A(\config{q}{\bot}, t, \config{q'}{\bot})$.
Let us denote by $b_\bot(q, q')$ this minimum.
By definition of $\leq_\oplus$, and since $\Semiring$ is total,
it holds that:
%
\begin{equation}\label{eq:bbot}
  b_\bot(q, q') = \bigoplus_{t\in \Delta^*}
  \textstyle
  \weight_A\bigl(\config{q}{\bot}, t, \config{q'}{\bot}\bigr).
\end{equation}
The infinite sum in~\eqref{eq:bbot} is well defined since $\Semiring$ is complete.
%
Following~\eqref{eq:SWVPA-value}, and the associativity and commutativity
and distributivity for~$\otimes$ and~$\oplus$, the minimum of~$A(t)$ is:
\begin{equation}\label{eq:min}
{\displaystyle\bigoplus_{t\in \Delta^*}} A(t)
=
{\displaystyle\bigoplus_{t\in \Delta^*}}
{\displaystyle\bigoplus_{q, q' \in Q}} \textstyle
\mathsf{in}(q) \mathop{\otimes}
\beta_{q, q'}(t)
\mathop{\otimes} \mathsf{out}(q')
=
{\displaystyle\bigoplus_{q, q' \in Q}} \textstyle
\mathsf{in}(q) \mathop{\otimes}
b_\bot(q, q')
\mathop{\otimes} \mathsf{out}(q')
\end{equation}

@@

Algorithm~\ref{algo:Dijkstra}
constructs iteratively two markings
$d_\bot : Q \times Q \to \Semiring$ and
$d_\top : Q \times P \times Q \to \Phic$,
%of the triplets $\<q, \sigma, q'>$
%of states of $A$ by weight values in $\Semiring$,
that converges eventually to $b_\top$ and $b_\bot$.
%It uses for that purpose a priority queue $P$ containing triplets of
%$Q \times \{ \bot, \top \} \times Q$.
\florent{explication Fig.~\ref{fig:best-update} (update) suivant cas de \eqref{eq:SWVPA-weight}?}
The infinite sums in the updates of $d$ in Algorithm~\ref{algo:Dijkstra},
Figure~\ref{fig:best-update}
are well defined
since~$\Semiring$ is complete.
%
% COMPLEXITY
%The algorithm performs $2.|Q|^2$ iterations until $P$ is empty,
%and each iteration has a time complexity $O(|Q|^2 . |P|)$.
\florent{complexity: detail with      and states?}
%That gives a time complexity $O(|Q|^4 . |P|)$.
%It can be reduced by implementing $P$ as a priority queue,
%prioritized by the value returned by $d$.
%** where  $T$ is the worst time complexity for an oracle computing the values
%of Definition~\ref{def:effective}.
%$|Q|^3.\log(|Q|^2)$
%
Algorithm~\ref{algo:Dijkstra}
terminates in PTIME and at termination, $d_\bot = b_\bot$ and $d_\top = b_\top$.
\florent{(see Appendix~\ref{sec:bestsearch}).}
With~\eqref{eq:min}, this ensures
its correctness. %of Algorithm~\ref{algo:Dijkstra}.
%
\begin{figure}[ht]
For all $q_0, q_3 \in Q$, %$p \in P$,
\[
\begin{array}{lcl}
%\multicolumn{3}{l}{\mathrm{For~all~} q_0, q_3 \in Q, p \in P,}\\
d_\top(q_1, p, q_3) & \opluseq &
  d_\top(q_1, p, q_2) \otimes
  \displaystyle\bigoplus_{\Deltai} \weii(q_2, p, q_3)\\
%\multicolumn{3}{l}{\quad
%\mathrm{where~} \weii(q_2, p, q_3)_a \in \Phic
%\mathrm{~is~the~partial~application~}
%x_c \mapsto \weii(q_2, x_c, p, a, q_3)}\\
%
d_\bot(q_1, p, q_3) & \opluseq &
  d_\bot(q_1, q_2) \otimes
  \displaystyle\bigoplus_{\Deltai} \weiei(q_2, q_3)\\
%
d_\top(q_0, p, q_3) & \opluseq &
  {\displaystyle\bigoplus_{\Deltac}}^2
  \bigl[ \bigl( \weic(q_0, p, p', q_1) \otimes_2
  d_\top(q_1, p', q_2) \bigr) \otimes_2
  {\displaystyle\bigoplus_{\Deltar}} \weir(q_2, p', q_3) \bigr]\\
%\multicolumn{3}{l}{\quad
%\mathrm{where~} \weic(q_0, p, p', q_1)_{c'} \in \Phic
%\mathrm{~is~the~partial~application~}
%x_c \mapsto \weic(q_0, p, x_c, c', p', q_1)}\\[2pt]
%
d_\bot(q_0, q_3) & \opluseq &
  {\displaystyle\bigoplus_{\Deltac}}
  \bigl(
  \weiec(q_0, p, q_1) \otimes
   d_\top(q_1, p, q_2) \otimes
  \displaystyle\bigoplus_{\Deltar} \weir(q_2, p, q_3)\bigr)\\
%
d_\bot(q_1, q_3) & \opluseq &
  d_\bot(q_1, q_2) \otimes
  \displaystyle\bigoplus_{\Deltar} \weier(q_2, q_3)\\
%
d_\top(q_1, p, q_3) & \opluseq &
  d_\top(q_1, p, q_2) \otimes d_\top(q_2, p, q_3),
  \mathrm{if~} \< q_2, \top, q_3> \notin P \\
%
d_\bot(q_1, q_3) & \opluseq &
  d_\bot(q_1, q_2) \otimes d_\bot(q_2, q_3), \mathrm{if~} \< q_2, \bot, q_3> \notin P \\
\end{array}
\]
%$\weii(q_2, p, q_3)_a \in \Phic$, for $a \in \Deltai$,
%is the partial application
%$x_c \mapsto \weii(q_2, x_c, p, a, q_3)$.
%
%$\weic(q_0, p, p', q_1)_{c'} \in \Phic$, for $c' \in \Deltac$,
%is the partial application
%$x_c \mapsto \weic(q_0, p, x_c, c', p', q_1)$.
\caption{Update $d_\bot$ with $\<q_1, q_2>$ or $d_\top$ with $\< q_1, p, q_2>$.}
\label{fig:best-update}
\end{figure}
%
%\noindent
%** effectively computable by hypothesis that the label theory is effective**
%\florent{REVOIR}
Thanks to the hypothesis of effectiveness of $\bar\Phi$, 
it is possible to construct suring the iteration a witness word
for Proposition~\ref{th:best-search}, 
\ie a word of $\Delta^*$ with a minimal weight \wrt $A$.

@@

Let us now apply the models and results of the previous sections %in order to define
to the problem of parsing over an infinite alphabet. %appropriate
%
%\subsection{Definition}
%
Let~$\Sigma$
and~$\Delta = \Deltai \uplus \Deltac \uplus \Deltar$
be countable input and output alphabets,
let $\< \Semiring, \oplus, \zero, \otimes, \one>$ be a
commutative, bounded, total and complete %\florent{total?} 
semiring and let $\bar\Phi$ be an effective label theory over $\Semiring$,
containing $\Phi_\Sigma$, $\Phi_{\Sigma, \Deltai}$, as well as
$\Phii$, $\Phic$, $\Phir$, $\Phicr$
(following the notations of Section~\ref{sec:SWVPA-def}).
%
\noindent
We assume given the following input:
\begin{description}
\item[--] a \SWT $T$ over $\Sigma$, $\Deltai$, $\Semiring$, and $\bar\Phi$,
defining a measure %between words
$T: \Sigma^* \times \Deltai^* \to \Semiring$,

@@

This work can be extended in several directions. First, the
the best search algorithm could bbe generalized from $1$-best to $n$-best~\cite{Huang05kbest},
and to $k$-\emph{closed} semirings~\cite{Mohri02semiring}
(instead of \emph{bounded}, which corresponds to $0$-\emph{closed}). Second,
we believe that
the complexity bounds of the algorithms can be more precisely characterized.
Finally, the  best search algorithm presented here offline, whereas
an on-the-fly automata construction would allow for online parsing,
a suitable feature in the context of applications such as, e.g., automatic music transcription.
\florent{compare expressiveness with register etc automata}

@@

%\section{Correctness of the Best-Search Algorithm} \label{sec:bestsearch}
%\input{app-bestsearch}
